Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-11-17 Scripts/Initial_Analysis.Rmd
changes to legend

### Splitted Figure 3 for supplements

Note this chunk needs the previous one to be ran up to the forloop

@@

  p <- ggdraw() +
    draw_plot(eez_map, x = 0, y = 0.5, width = 1, height = 0.5) +
    # Regional boxplot
    draw_plot(land_map, x = 0, y = 0, width = 1, height = 0.5) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                    size = 20,
                    x = c(0, 0), 
                    y = c(0.98, 0.46)
    ) + 
  theme(plot.background = element_rect(fill="white", color = NA))

>>>>

###### Splitted Figure 3 for supplements

Note this chunk needs the previous one to be ran up to the for-loop

Year of change in the shared distribution of 4,119 transboundary stocks and their contribution to fishing revenue. A) Contribution of shifting stocks to a country or territory's total fishing revenue from transboundary stocks. B) Average year of range shift across an EEZ’s transboundary stocks. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue. This figure is a detached version of Figure 3

@@

  p <- ggdraw() +
    draw_plot(eez_map, x = 0, y = 0, width = 1, height = 0.5) +
    # Regional boxplot
    draw_plot(land_map, x = 0, y = 0.5, width = 1, height = 0.5) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                    size = 20,
                    x = c(0, 0), 
                    y = c(0.98, 0.46)
    ) + 
  theme(plot.background = element_rect(fill="white", color = NA))

### 2021-11-17 Scripts/Manuscript.Rmd
changes to legend

```{r toeFigure2, eval = T,  echo = F, fig.width  = 13,fig.pos= "H", fig.height =11, fig.cap =  "Year of change in the shared distribution of 4,119 transboundary stocks. A) Land polygons show the contribution of shifting stocks to a country or territory’s total fishing revenue from transboundary stocks. Exclusive Economic Zone polygons display average year of range shifts within them. Warm colors are indicative of an early shift/high fishing revenue contribution from transboundary stocks while cool colors represent a late shift/low fishing revenue. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue. B) Year of shared distribution shifts by UN sub-regions. Points color coded by the median year for all shifting stocks in the region. Horizontal dashed line represents the year by which countries have committed to reach full implementation of the 2030 Agenda. N = North, S = South, W = West and E = East. Ltn. Ame. and the Car. = Latin America and the Caribbean. Aus and New Z. = Australia and New Zealand."}

>>>>

```{r toeFigure2, eval = T,  echo = F, fig.width  = 13,fig.pos= "H", fig.height =11, fig.cap =  "Year of change in the shared distribution of 4,119 transboundary stocks. A) Land polygons show the contribution of shifting stocks to a country or territory’s total fishing revenue from transboundary stocks. Exclusive Economic Zone polygons display average year of range shifts within them. Warm colors are indicative of an early shift/high fishing revenue contribution from transboundary stocks while cold colors represent a late shift/low fishing revenue. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue. B) Year of shared distribution shifts by UN sub-regions. Points color coded by the median year for all shifting stocks in the region. Horizontal dashed line represents the year by which countries have committed to reach full implementation of the 2030 Agenda. N = North, S = South, W = West and E = East. Ltn. Ame. and the Car. = Latin America and the Caribbean. Aus and New Z. = Australia and New Zealand."}
